Raw Data Comparison

### 2019-09-11 Raw Data Comparison.Rmd
...

  disp = full_join(
           full_join( as_tibble(t(means), rownames='sample') %>% rename(V1='mean'), 
                      as_tibble(t(sds), rownames='sample') %>% rename(V1='sd'), by='sample'),
           full_join(as_tibble(t(vars), rownames='sample') %>% rename(V1='var'),
                     as_tibble(t(iqrs), rownames='sample') %>% rename(V1='IQR'), by='sample'), 
           by='sample') 
  return(disp)
}

@@

>>>>

  disp = full_join(
           full_join( as_tibble(t(means), rownames='sample') %>% dplyr::rename('mean' = 'V1'), 
                      as_tibble(t(sds), rownames='sample') %>% dplyr::rename('sd' = 'V1'),  by='sample'),
           full_join(as_tibble(t(vars), rownames='sample') %>% dplyr::rename('var' = 'V1'), 
                     as_tibble(t(iqrs), rownames='sample') %>% dplyr::rename('IQR' = 'V1'),  by='sample'), 
           by='sample') 
  return(disp)
}

@@

## Retrained model, no scaling

Shows nearly the same problem as before.  The variance is clearly at issue.

preds = do.call(bind_rows, purrr::map(
  list.files('~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf/predictions_no_scale/0.9/', pattern='predictions.tsv', recursive = T, full.names = T), 
  function(f) read_tsv(f, col_types = 'cddcccccccc'))) %>% mutate(Endoscopy = as.Date(Endoscopy)) %>% dplyr::select(-`Path Notes`)

# FNR is still over 50% in the old progressors as well
nrow(preds %>% filter(Status == 'P' & Risk == 'Low' & !grepl('OCCAMS',`Hospital Research ID`)))/nrow(preds %>% filter(Status == 'P' &  !grepl('OCCAMS',`Hospital Research ID`)))
```
```
